Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic

### 2024-07-10 README.qmd
PHEW recreate google doc version + targetsify + renvify + clean up website

# manuscript_target <- targets::tar_read(manuscript)

# yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))
# title <- yaml_metadata$title
# abstract <- yaml_metadata$abstract

title <- "Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic"
abstract <- "TODO"
```

>>>>

manuscript_target <- targets::tar_read(manuscript)

yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))
title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
```

### 2024-07-10 analysis/analysis-misc.qmd
PHEW recreate google doc version + targetsify + renvify + clean up website

---
title: "Other analysis"
format:
  html:
    code-tools: false
    include-in-header: 
      - text: |
          <style>
          .table th {
            font-weight: bold
          }
          </style>
---

@@

```{r}
#| label: fig-derogation-map
#| fig-width: 6.5
#| fig-height: 3.5
#| out-width: 100%
#| fig-cap: "ICCPR pandemic-related derogations"

@@

```{r}
#| label: fig-panback-map
#| fig-width: 6.5
#| fig-height: 3.5
#| out-width: 100%
#| fig-cap: "Average Pandemic Backsliding Index from V-Dem from March 2020–June 2021"

@@

# Treaty actions by state and type

```{r}
#| label: fig-treaty-action-state-type
#| fig-width: 6.5
#| fig-height: 4

>>>>

---
title: "Miscellaneous analysis"
format:
  html:
    code-fold: true
---

@@

```{r}
#| label: figure-derogation-map
#| fig-width: 6.5
#| fig-height: 3.5
#| out-width: 100%
#| fig-cap: "ICCPR pandemic-related derogations"

@@

```{r}
#| label: figure-panback-map
#| fig-width: 6.5
#| fig-height: 3.5
#| out-width: 100%
#| fig-cap: "Average Pandemic Backsliding Index from V-Dem from March 2020–June 2021"

@@

### Non-derogation treaty actions

```{r}
#| label: figure-treaty-action-state-type
#| fig-cap: Counts of human rights treaty actions from March 2020–June 2021
#| fig-width: 6.5
#| fig-height: 4
#| out-width: 100%

### 2024-07-10 analysis/appendix.qmd
PHEW recreate google doc version + targetsify + renvify + clean up website

TODO

>>>>

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
targets::tar_load(c(manuscript))
```

```{=html}
<p class="text-center">
  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/appendix.html" target="appendix">
  <i class="fa-solid fa-file-lines"></i> &ensp;HTML
  </a>

  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/appendix.html" target="_blank">
  <i class="fa-solid fa-arrow-up-right-from-square"></i>&ensp;HTML <small>(new window)</small>
  </a>

  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/appendix.pdf" target="appendix">
  <i class="fa-solid fa-file-pdf"></i>&ensp;PDF
  </a>

  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/appendix.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;PDF <small>(download)</small>
  </a>

  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output/appendix+ms.pdf" target="appendix">
  <i class="fa-solid fa-file-pdf"></i>&ensp;Manuscripty PDF
  </a>

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/appendix+ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>
</p>

<iframe src="/manuscript/output/appendix.html" frameborder="0" style="overflow:hidden;height:90%;width:100%;border:2px solid #ccc;" height="90%" width="100%" name="appendix"></iframe>
```

### 2024-07-10 analysis/hypotheses.qmd
PHEW recreate google doc version + targetsify + renvify + clean up website

---
title: "Hypotheses"
format:
  html:
    code-tools: false
    include-in-header: 
      - text: |
          <style>
          .table th {
            font-weight: bold
          }
          </style>
---

@@

library(tidyverse)
library(tidybayes)
library(modelsummary)
library(marginaleffects)
library(scales)
library(tinytable)
library(ggh4x)
library(targets)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

tar_load(c(m_derogations, m_tbl_derogations))
tar_load(c(m_restrictions, m_tbl_restrictions))
tar_load(c(m_econ, m_tbl_econ))
tar_load(c(m_hr, m_tbl_hr))

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))
```

# Expectations / hypotheses

```{r}
#| label: tbl-expectations
#| tbl-cap: "Expectations about state transparency and practices during COVID-19"

@@

tbl |> 
  tt(width = c(1, 2, 2)) |> 
  format_tt(j = 2:3, markdown = TRUE) |> 
  style_tt(j = 1:3, align = "lll") |> 
  style_tt(j = 1, bold = TRUE) |> 
  style_tt(
    bootstrap_class = "table table-sm"
  )
```

- H~1~: States will be more likely to issue derogations during COVID-19 if they have strong rule of law.
- H~2~: Regime transitioning states, including backsliders, will be more likely to issue derogations.
- H~3~: If a state derogates from ICCPR, we expect that they will take the pandemic more seriously and be more likely to issue pandemic-related restrictions.
- H~4~: States experiencing democratic backsliding will be more likely to abuse human rights.
- H~5~: States experiencing democratic backsliding that also issue derogations will be less likely to abuse human rights than states that only backslide.

# Explaining derogations (H~1~ and H~2~)

## Derogations predicted with backsliding (PanBack)

::: {.callout-tip}
### Quick interpretation

States that experienced democratic backsliding were more likely to derogate, but only by a little
:::

```{r}
#| label: fig-derog-panback

preds_derog_panback <- m_derogations$m_derogations_panback |> 
  epred_draws(
    datagrid(model = m_derogations$m_derogations_panback, panback = seq(0, 1, 0.1)), 
    ndraws = 500, seed = 1234)

ggplot(preds_derog_panback, aes(x = panback, y = .epred)) +
  stat_lineribbon(alpha = 0.4, fill = clrs[5], color = clrs[5]) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  labs(
    x = "Pandemic backsliding index (PanBack)", 
    y = "Posterior probability of derogation",
    fill = "Internal movement measures"
  ) +
  theme_pandem()
```

## Derogations predicted with violations of democratic standards (PanDem)

::: {.callout-tip}
### Quick interpretation

States that had worse violations of democratic standards were less likely to derogate, but the difference is not really substanial (0.5%ish chance when PanDem is 0; 0.15%ish chance when PanDem is 1)
:::

```{r}
#| label: fig-derog-pandem

preds_derog_pandem <- m_derogations$m_derogations_pandem |> 
  epred_draws(
    datagrid(model = m_derogations$m_derogations_pandem, pandem = seq(0, 1, 0.1)), 
    ndraws = 500, seed = 1234)

ggplot(preds_derog_pandem, aes(x = pandem, y = .epred)) +
  stat_lineribbon(alpha = 0.4, fill = clrs[8], color = clrs[8]) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  labs(
    x = "Pandemic violations of democratic standards index (PanDem)", 
    y = "Posterior probability of derogation",
    fill = "Internal movement measures"
  ) +
  theme_pandem()
```

## Table

```{r}
#| label: tbl-results-full-derogations

notes <- paste(
  "Note: Estimates are median posterior odds ratios from logistic regression models;",
  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
)

m_tbl_derogations |> 
  set_names(NULL) |>
  modelsummary(
    exponentiate = TRUE,
    estimate = "{estimate}",
    statistic = "[{conf.low}, {conf.high}]",
    coef_map = coef_map,
    gof_map = gof_map,
    output = "tinytable",
    fmt = fmt_significant(2),
    notes = notes,
    width = c(0.4, rep(0.3, 2))
  ) |> 
  group_tt(j = list("ICCPR derogation filed" = 2:3))
```

# Explaining restrictions (H~3~)

## Internal movement restrictions

::: {.callout-tip}
### Quick interpretation

States with no backsliding that did not derogate were most likely to have no internal movement restrictions

Non-backsliding states that derogated look roughly like backsliding states that didn't derogate—similar probabilities of severity of internal movement measures.

Backsliding states that derogated were overwhelmingly likely to have restrictions in place.
:::

```{r}
#| label: fig-restrictions-movement

preds_movement <- m_restrictions$m_restrict_movement |> 
  epred_draws(
    datagrid(model = m_restrictions$m_restrict_movement, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

ggplot(preds_movement, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = .category), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 4, 2)]) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Internal movement measures") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "top", legend.position = "top")
```

## Public transportation restrictions

::: {.callout-tip}
### Quick interpretation

Non-backsliding states that didn't derogate are more likely to have no public transportation measures; non-backsliding states that did derogate were most likely to recommend or require closing

Backsliding states have similar probabilities of public transportation measures across derogation status—no substantial difference between derogating and non-derogating states
:::

```{r}
#| label: fig-restrictions-pubtrans

preds_pubtrans <- m_restrictions$m_restrict_pubtrans |> 
  epred_draws(
    datagrid(model = m_restrictions$m_restrict_pubtrans, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

ggplot(preds_pubtrans, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = .category), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 4, 2)]) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Public transportation measures") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "top", legend.position = "top")
```

## Stay at home restrictions

::: {.callout-tip}
### Quick interpretation

Non-backsliding states that didn't derogate are more likely to have no stay at home measures

Non-backsliding states that derogated look roughly like backsliding states that didn't derogate—similar probabilities of severity of stay at home measures.

Backsliding states that derogated were overwhelmingly likely to have restrictions in place.
:::

```{r}
#| label: fig-restrictions-stayhome

preds_stayhome <- m_restrictions$m_restrict_stayhome |> 
  epred_draws(
    datagrid(model = m_restrictions$m_restrict_stayhome, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

ggplot(preds_stayhome, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = .category), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 4, 2, 1)], guide = guide_legend(nrow = 2)) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Stay at home measures") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "top", legend.position = "top")
```

## Table

```{r}
#| label: tbl-results-full-restrictions

notes <- paste(
  "Note: Estimates are median posterior odds ratios from ordered logistic regression models;",
  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
)

m_tbl_restrictions |> 
  set_names(c("Movement", "Close public transit", "Stay at home")) |> 
  modelsummary(
    exponentiate = TRUE,
    estimate = "{estimate}",
    statistic = "[{conf.low}, {conf.high}]",
    coef_map = coef_map,
    gof_map = gof_map,
    output = "tinytable",
    fmt = fmt_significant(2),
    notes = notes,
    width = c(0.3, rep(0.23, 3))
  )
```

# Explaining COVID-19 economic policies (no hypotheses)

## Income support

::: {.callout-tip}
### Quick interpretation

Non-backsliding states have the same patterns in the probability of different types of income support regardless of derogations.

Among backsliding states, those that didn't derogate are have a nearly 100% chance of providing no income support; those that did derogate were more likely to provide some level of income support than non-backsliding states.
:::

```{r}
#| label: fig-econ-income

preds_econ_income <- m_econ$m_econ_income |> 
  epred_draws(
    datagrid(model = m_econ$m_econ_income, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

ggplot(preds_econ_income, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = fct_rev(.category)), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 4, 2, 1)], guide = guide_legend(nrow = 3)) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Income support") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "top", legend.position = "top")
```

## Debt relief

::: {.callout-tip}
### Quick interpretation

Non-backsliding states that derogated were more likely than non-derogating states to provide broad debt relief.

Backsliding states that didn't derogate had a nearly 100% chance of providing broad debt relief while those that derogated roughly match the patterns of non-backsliding derogating states.

For backsliders this is the reverse of the income support finding, but that's most likely because the handful of derogating backsliders all used the same policies: no income support, yes debt relief.
:::

```{r}
#| label: fig-econ-debt

preds_econ_debt <- m_econ$m_econ_debt |> 
  epred_draws(
    datagrid(model = m_econ$m_econ_debt, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

ggplot(preds_econ_debt, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = fct_rev(.category)), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 4, 2, 1)], guide = guide_legend(nrow = 1)) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Debt relief") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "left", legend.position = "top")
```

## Table

```{r}
#| label: tbl-results-full-econ

notes <- paste(
  "Note: Estimates are median posterior odds ratios from ordered logistic regression models;",
  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
)

m_tbl_econ |> 
  set_names(c("Income support", "Debt relief")) |> 
  modelsummary(
    exponentiate = TRUE,
    estimate = "{estimate}",
    statistic = "[{conf.low}, {conf.high}]",
    coef_map = coef_map,
    gof_map = gof_map,
    output = "tinytable",
    fmt = fmt_significant(2),
    notes = notes,
    width = c(0.4, rep(0.3, 2))
  )
```

# Explaining COVID-19 human rights violations (H~4~ and H~5~)

## Discriminatory policy

::: {.callout-tip}
### Quick interpretation

Among non-backsliding states, derogation seems to matter a lot. Both derogators are non-derogators are most likely to not use discriminatory policies, but those that don't derogate have non-trivial probabilities of minor and major discriminatory policies while those that do derogate have a nearly 100% chance of no discriminatory policies.

Among backsliders, those that derogated also have essentially a 100% chance of no discriminatory policies, while those that didn't derogate have a nearly 100% chance of major discrimination. 
:::

```{r}
#| label: fig-hr-discrim

preds_hr_discrim <- m_hr$m_hr_discrim |> 
  epred_draws(
    datagrid(model = m_hr$m_hr_discrim, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

ggplot(preds_hr_discrim, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = .category), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 4, 2, 1)]) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Discrimintaory policy") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "left", legend.position = "top")
```

## Non-derogable rights

::: {.callout-tip}
### Quick interpretation

Among non-backsliding states, derogation again to matter a lot. Both derogators are non-derogators are most likely to not violate non-derogable rights, but those that didn't derogate have a higher probability of major violations. Those that do derogate have a nearly 100% chance of no violations.

Backsliders have a nearly 100% chance of violating non-derogable rights regardless of derogation.
:::

```{r}
#| label: fig-hr-ndrights

preds_hr_ndrights <- m_hr$m_hr_ndrights |> 
  epred_draws(
    datagrid(model = m_hr$m_hr_ndrights, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

preds_hr_ndrights_plot <- bind_rows(
  preds_hr_ndrights |> mutate(.category = "Major"),
  preds_hr_ndrights |> mutate(.category = "None") |> mutate(.epred = 1 - .epred)
) |> 
  mutate(.category = factor(.category, levels = c("None", "Major"), ordered = TRUE))

ggplot(preds_hr_ndrights_plot, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = .category), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 1)]) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Abusive enforcement") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "left", legend.position = "top")
```

## Abusive enforcement

::: {.callout-tip}
### Quick interpretation

*This one is interesting and weird?*

Among non-backsliding states, derogation again matters, but it's less protective here than for the other human rights issues. Non-derogators have the highest probability of no abusive enforcement (75%ish), with low probabilities of higher levels. Derogators, on the other hand, see a lot more variation in abusive enforcement, with only a 50%ish percent chance of no abuse (and the other levels spread across the other 50%).

For backsliding states, the same pattern holds. Non-derogating backsliding states look basically like non-derogating non-backsliders, just with more uncertainty (with a 75%ish probability of no abusive enforcement). Derogating backsliders only have a 25%ish chance of no abuse—the other levels are spread across the remaining 75%.

Derogation enables more abusive enforcement?
:::

```{r}
#| label: fig-hr-abusive

preds_hr_abusive <- m_hr$m_hr_abusive |> 
  epred_draws(
    datagrid(model = m_hr$m_hr_abusive, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

ggplot(preds_hr_abusive, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = .category), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 4, 2, 1)]) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Abusive enforcement") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "left", legend.position = "top")
```

## No time limited measures

::: {.callout-tip}
### Quick interpretation

For non-backsliders, among non-derogators there's a 75%ish chance of not not having time limited measures (i.e. having time limited measures; the good outcome); for derogators that jumps to 90%ish.

(This makes sense since derogations require specified time limits.)

For backsliders, there's a 100% chance of having time limited measures for both derogators and non-derogators.
:::

```{r}
#| label: fig-hr-nolimit

preds_hr_nolimit <- m_hr$m_hr_nolimit |> 
  epred_draws(
    datagrid(model = m_hr$m_hr_nolimit, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

preds_hr_nolimit_plot <- bind_rows(
  preds_hr_nolimit |> mutate(.category = "Moderate"),
  preds_hr_nolimit |> mutate(.category = "None") |> mutate(.epred = 1 - .epred)
) |> 
  mutate(.category = factor(.category, levels = c("None", "Moderate"), ordered = TRUE))

ggplot(preds_hr_nolimit_plot, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = .category), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 2)]) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "No time limited measures") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "left", legend.position = "top")
```

## Media restrictions

::: {.callout-tip}
### Quick interpretation

For non-backsliders, derogations help; non-derogators have only a 25% chance of no media restrictions and a 55%ish chance of major media restrictions.

For backsliders, derogations don't do anything—there's a 100% chance of major media restrictions for both derogators and non-derogators.
:::

```{r}
#| label: fig-hr-media

preds_hr_media <- m_hr$m_hr_media |> 
  epred_draws(
    datagrid(model = m_hr$m_hr_media, derogation_ineffect = unique, panbackdichot = unique), 
    ndraws = 500, seed = 1234) |> 
  ungroup() |> 
  mutate(
    derogation_ineffect = factor(derogation_ineffect, labels = c("No derogation", "Derogation"), ordered = TRUE),
    panbackdichot = factor(panbackdichot, labels = c("No backsliding", "Backsliding"), ordered = TRUE)
  )

ggplot(preds_hr_media, aes(x = .draw, y = .epred)) +
  geom_area(aes(fill = .category), position = position_stack()) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(7, 4, 2, 1)]) +
  labs(
    x = NULL, y = "Cumulative outcome probabilities",
    fill = "Media restrictions") +
  facet_nested_wrap(
    vars(panbackdichot, derogation_ineffect),
    strip = strip_nested(background_x = list(element_rect(fill = "grey92"), NULL), by_layer_x = TRUE),
    nrow = 1
  ) +
  theme_pandem() +
  theme(legend.title.position = "left", legend.position = "top")
```

## Table

```{r}
#| label: tbl-results-full-hr

notes <- paste(
  "Note: Estimates are median posterior odds ratios from logistic and ordered logistic regression models;",
  "95% credible intervals (highest density posterior interval, or HDPI) in brackets."
)

m_tbl_hr |> 
  set_names(
    c("Discriminatory policy", "Non-derogable rights", 
      "Abusive enforcement", "No time limits", "Media restrictions"
    )
  ) |>
  modelsummary(
    exponentiate = TRUE,
    estimate = "{estimate}",
    statistic = "[{conf.low}, {conf.high}]",
    coef_map = coef_map,
    gof_map = gof_map,
    output = "tinytable",
    fmt = fmt_significant(2),
    notes = notes,
    width = c(0.2, rep(0.16, 5))
  )
```

>>>>

---
title: "Hypotheses"
format:
  html:
    code-fold: true
---

@@

library(tidyverse)
library(tinytable)
```

```{r}
#| label: table-expectations
#| tbl-cap: "Expectations about state transparency and practices during COVID-19"

@@

tbl |>
  tt(width = c(1, 2, 2)) |>
  format_tt(j = 2:3, markdown = TRUE) |>
  style_tt(j = 1:3, align = "lll") |>
  style_tt(i = seq(1, 5, by = 2), j = 1, bold = TRUE, rowspan = 2, alignv = "t") |>
  style_tt(
    bootstrap_class = "table table-sm"
  )
```

- **H~1~**: States experiencing democratic backsliding will be more likely to issue derogations.
- **H~2~**: States experiencing democratic backsliding will be more likely to abuse human rights.
- **H~3~**: States experiencing democratic backsliding that also issue derogations will be less likely to abuse human rights than states that only backslide.

### 2024-07-10 analysis/targets.qmd
PHEW recreate google doc version + targetsify + renvify + clean up website

---
title: "Targets pipeline"
format:
  html:
    code-fold: true
---

TODO

>>>>

---
title: "{targets} pipeline"
freeze: false
format:
  html:
    code-fold: true
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  # echo = FALSE, include = FALSE, warning = FALSE, message = FALSE,
  fig.width = 6, fig.height = (6 * 0.618), out.width = "80%",
  fig.align = "center", fig.retina = 3,
  collapse = TRUE
)

options(digits = 3, width = 120, dplyr.summarise.inform = FALSE)
```

We use [the magical {targets} package](https://docs.ropensci.org/targets/) to run our analysis and keep track of all dependencies automatically.

To build the entire project, run `targets::tar_make()` at the R console.

Here's our complete pipeline:

```{r}
#| label: show-targets-pipeline
#| echo: false

withr::with_dir(here::here(), {
  targets::tar_glimpse()
})
```

### 2024-07-10 index.qmd
PHEW recreate google doc version + targetsify + renvify + clean up website

```{r echo=FALSE}
# yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))
# title <- yaml_metadata$title
# abstract <- yaml_metadata$abstract

title <- "Derogations, Democratic Backsliding, and International Human Rights During the COVID-19 Pandemic"
abstract <- "TODO"
```

>>>>

```{r echo=FALSE}
yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))
title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
```
